### 2023-03-27 seitan/seitan.tex
last important changes

With the last week of their month-long vax celebration trip,
the protagonist visits two other ThursDz friends in Raleigh.
They speedrun Celeste (a nervous cat who never shows affection to strangers, except nonbinary people).
Said friends are themselves a little like cats, visibly changed by their own quarantine experiences.
All three humans are eager to share whatever fruits said experiences have borne.
One of them is you.

You, Seitan Reloaded, are not seitan wings.
You are sausage, strongly spiced, in need of no sauce,
to be put on scrambled eggs or pizza or simply to be eaten unadorned and cold from the fridge.
Your author demonstrates you to the protagonist.
He puts half a cup of paprika into you.
He pours soy sauce into you, and keeps pouring -- the protagonist agog -- for impossibly long.
He kneads you,
and the protagonist remarks that they were afraid to knead their own because it already came out so tough,
and he remarks that the olive oil and the nooch inside you help disrupt gluten formation,
% so even with all the kneading it comes out pretty tender,
and they think ah, this might be the final piece of the puzzle.

@@

You tell them the preceding 4 chapters,
and they agree to share with you the honor of putting the pieces together,
and that is the story of how seitan wings were made correctly in Santa Barbara for the first time ever.

\vspace{15em}

>>>>

With the last week of their month-long vax celebration trip,
the protagonist visits two other ThursDz friends in Raleigh RTP USA.
They speedrun Celeste (a nervous cat who never shows affection to strangers, except nonbinary people).
Said friends are themselves a little like cats, visibly changed by their own quarantine experiences.
All three humans are eager to share whatever fruits said experiences have borne.
One of them is you.

You, Seitan Reloaded, are not wings.
You are sausage, strongly spiced, fierce, in need of no sauce,
to be put on scrambled eggs or pizza or simply to be eaten unadorned and cold from the fridge.
Your author demonstrates you to the protagonist.
He puts half a cup of paprika into you.
He pours soy sauce into you, and keeps pouring -- the protagonist agog -- for impossibly long.
He kneads you,
and the protagonist remarks that they were afraid to knead their own because it already came out so tough,
and he remarks that the olive oil and the nooch inside you help disrupt gluten formation,
% so even with all the kneading it comes out pretty tender,
and they think ah, this might be the final piece of the puzzle.

@@

You tell them the preceding 4 chapters,
and they agree to share with you the honor of putting the pieces together,
and you even make half with noncanonical sauce because your dad can't have spicy anymore,
and that is the story of how seitan wings were made correctly in Santa Barbara for the first time ever.

\vspace{14em}
